---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`nlpred`

[![Travis-CI Build Status](https://travis-ci.org/benkeser/nlpred.svg?branch=master)](https://travis-ci.org/benkeser/nlpred)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/benkeser/nlpred?branch=master&svg=true)](https://ci.appveyor.com/project/benkeser/nlpred)
[![Coverage Status](https://img.shields.io/codecov/c/github/benkeser/nlpred/master.svg)](https://codecov.io/github/benkeser/nlpred?branch=master)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![MIT license](http://img.shields.io/badge/license-MIT-brightgreen.svg)](http://opensource.org/licenses/MIT)
<!-- [![CRAN](http://www.r-pkg.org/badges/version/nlpred)](http://www.r-pkg.org/pkg/nlpred) -->
<!-- [![CRAN downloads](https://cranlogs.r-pkg.org/badges/nlpred)](https://CRAN.R-project.org/package=nlpred) -->
<!-- [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.835868.svg)](https://doi.org/10.5281/zenodo.835868) -->

> Small-sample optimized estimators of cross-validated prediction metrics

[David Benkeser](https://www.benkeserstatistics.com/) 

---

## Description

`nlpred` is an R package for computing estimates of cross-validated prediction metrics. These estimates are tailored for superior performance in small samples. Several estimators are available including ones based cross-validated targeted minimum loss-based estimation, estimating equations, and one-step estimation. 

---

## Installation

For standard use, we recommend installing the package from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("nlpred")
```

You can install the current release of `nlpred` from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/) with:

```{r gh-installation, eval = FALSE}
devtools::install_github("benkeser/nlpred")
```
---

## Usage

The main functions in the package are `cv_auc` and `cv_scrnp`, which are used to 
compute, respectively, the `K`-fold [cross-validated area under the receiver operating
characteristics curve](http://projecteuclid.org/euclid.ejs/1437742107) (CVAUC) and 
the `K`-fold cross-validated [sensitivity constrained rate of negative prediction](https://onlinelibrary.wiley.com/doi/abs/10.1002/sim.7296). However, rather than using
standard cross-validation estimators (where prediction algorithms are developed in a 
training sample and AUC/SCRNP estimated using the validation sample), we instead use
techniques from efficiency theory to estimate these quantities. This allows us to use
the training data both to develop the prediction algorithm, *as well as* key nuisance 
parameters needed to evaluate AUC/SCRNP. By reserving more data for estimation of these
key parameters, we obtain improved performance in small samples. 

```{r}
# load package
library(nlpred)

# turn off messages from np package
options(np.messages=FALSE)

# simulate data
n <- 200
p <- 10
X <- data.frame(matrix(rnorm(n*p), nrow = n, ncol = p))
Y <- rbinom(n, 1, plogis(X[,1] + X[,10]))

# get cv auc estimates for logistic regression
logistic_cv_auc_ests <- cv_auc(Y = Y, X = X, K = 5, learner = "glm_wrapper")
logistic_cv_auc_ests

# get cv auc estimates for random forest using nested 
# cross-validation for nuisance parameter estimation. nested
# cross-validation is unfortunately necessary when aggressive learners 
# are used. 
rf_cv_auc_ests <- cv_auc(Y = Y, X = X, K = 5, 
						 learner = "randomforest_wrapper", 
						 nested_cv = TRUE)
rf_cv_auc_ests

# same examples for scrnp
logistic_cv_scrnp_ests <- cv_scrnp(Y = Y, X = X, K = 5, learner = "glm_wrapper")
logistic_cv_scrnp_ests


rf_cv_scrnp_ests <- cv_scrnp(Y = Y, X = X, K = 5, 
						 learner = "randomforest_wrapper", 
						 nested_cv = TRUE)
rf_cv_scrnp_ests
```

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/benkeser/nlpred/issues).

---

## Contributions

Interested contributors can consult our [`contribution guidelines`](https://github.com/benkeser/nlpred/blob/master/CONTRIBUTING.md) prior to submitting a pull request.

---

## Citation 

## License

&copy; 2019 [David Benkeser](http://www.benkeserstatistics.com)

The contents of this repository are distributed under the MIT license. See
below for details:
```
The MIT License (MIT)

Copyright (c) 2019 David C. Benkeser

Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.
```
